---
title: "Obtaining lists of articles that cite RCTs"
author: "Lars Vilhuber"
date: "`r Sys.Date()`"
output: 
  html_document: 
    keep_md: yes
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Overview

## Sources

- CrossRef

```{r config_libs,include=FALSE,message=FALSE}
source(file.path(rprojroot::find_root(rprojroot::has_file("pathconfig.R")),"pathconfig.R"),echo=TRUE)
source(file.path(basepath,"global-libraries.R"),echo=FALSE)
source(file.path(programs,"libraries.R"), echo=FALSE)
source(file.path(programs,"config.R"), echo=FALSE)
```

## Instructions
This file, when executed, will

- download a list of articles for top journals from CrossRef
- Filter those articles by whether they cite RCTs or not
- Save the output as CSV

The program will check for prior files, and will NOT download new data if those files are present. Thus, to get a fresh run, 

- delete ` `r issns.file` ` if you want to re-start the whole process (which stores the last query date, and is updated at the end of this process)
- delete ` `doi.file.Rds` ` if you want to update to re-query CrossRef (um, this might not yet work)

## Data locations


Temporary data is in

> `r interwrk`

and can (should) be deleted after completion.

## In-scope journals

We look at all major econ journals, identified here by ISSN.

```{r issn}
source(file.path(programs,"01_create_issn.R"), echo= TRUE)

```

## Getting all articles

Now read DOI for all later dates. This is safe to re-run, it will only get newer records when re-run. A full pull with 24 years of data may take `690.044 sec` (example run).

```{r get_articles}
source(file.path(programs,"02_get_articles_cr.R"), echo= TRUE)
```

We read **`r nrow(new.df %>% select(doi) %>% distinct())`** article records for **`r nrow(new.df %>% select(container.title) %>% distinct())`** journals. 

## Filtering out irrelevant articles

We filter out editorials, technical publications (which all have DOIs):

```{r filter_articles}
source(file.path(programs,"03_filter_articles.R"),echo=TRUE)
```


This leaves us with **`r nrow(filtered.df %>% select(doi) %>% distinct())`** article records for **`r nrow(filtered.df %>% select(container.title) %>% distinct())`** journals. 

## Assessing the references

Now let's focus on the references that CrossRef provides:

```{r get_refs}
source(file.path(programs,"04_inspect_refs.R"),echo=TRUE)

```


Of the `r nrow(refs.df)` references listed, 

- `r refs.df %>% filter(has_rct_in_refs) %>% nrow()` point to RCTs at the AEA Registry in the structured references
- `r refs.df %>% filter(has_rct_in_citations) %>% nrow() ` point to RCTs in the unstructured (unparsed) references
- `r refs.df %>% filter(has_rct_broken_ref) %>% nrow() ` have a weird reference that does not resolve (in the `journal.title` field)

Overall, we find `r refs.df %>% filter(has_rct_ref) %>% distinct(doi) %>% nrow()` articles that have an actionable link to AEA RCT DOIs. An additional `r refs.df %>% filter(has_ssr_link) %>% distinct(doi) %>% nrow()` have a URL in the references that points to `sociascienceregistry.org`.



## System info

```{r sysinfo}
Sys.info()
```
