---
title: "Obtaining lists of articles that cite RCTs"
author: "Lars Vilhuber"
date: "`r Sys.Date()`"
output: 
  html_document: 
    keep_md: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Overview

## Sources

- CrossRef

```{r config_libs,include=FALSE,message=FALSE}
source(file.path(rprojroot::find_root(rprojroot::has_file("pathconfig.R")),"pathconfig.R"),echo=TRUE)
source(file.path(basepath,"global-libraries.R"),echo=TRUE)
source(file.path(basepath,"config.R"),echo=TRUE)
```

## Instructions
This file, when executed, will

- download a list of articles for top journals from CrossRef
- Filter those articles by whether they cite RCTs or not
- Save the output as CSV

The program will check for prior files, and will NOT download new data if those files are present. Thus, to get a fresh run, 

- delete ` `r full.file.Rds` ` if you want to re-start the whole process
- delete ` `r file.path(interwrk,paste0("new.Rds"))` ` to re-download files from CrossRef
- revert ` `r issns.file` ` (which stores the last query date, and is updated at the end of this process)

## Data locations

Permanent data is in

> `r dataloc`

and should be committed to the repository.

Temporary data is in

> `r interwrk`

and can (should) be deleted after completion.

## In-scope journals

We look at all major econ journals, identified here by ISSN.

```{r issn}
source(file.path(programs,"01_create_issn.R"), echo= TRUE)

```

Now read DOI for all later dates.

```{r get_articles}
source(file.path(programs,"02_get_articles_cr.R"), echo= TRUE)
```

We read **`r nrow(new.df %>% select(doi) %>% distinct())`** article records for **`r nrow(new.df %>% select(container.title) %>% distinct())`** journals, with **`r nrow(new.df)`** article-author observations:

```{r stats1, echo=FALSE}
knitr::kable(new.df %>% group_by(container.title) %>% summarise(records = n()))
```

## System info

```{r sysinfo}
Sys.info()
```
